---
title: "linear model from Web"
author: "Martha Leal Olmedo"
date: "November 22 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

Based on the scatter plot above, If you were to draw a straight line on the points. You will see that most of them are increasing and that the points are moved towards the right. So I think its a positive correlation.

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```

### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The information above shows us that the residual standard error is 1.226. And that the adjusted r squared is 0.467. It also shows us that the fit equation is SIMS=0.054563*ARM-4.095160.


#### Predict at target point
SIMS=0.054563*ARM-4.095160
```{r}
0.054563*88-4.095160
```

When 88 was plugged in for ARM we got 0.706384, this is the prediction for the value.

```{r}
new<-data.frame(ARM = 88,GRIP = 94)
```

```{r}
predict(model.1,new, interval = "prediction")
```


#### scatterplot with model fit
```{r}
basicNN <-ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm)
```
  
The scatter plot above shows us the best fit line for our data, we can see that if we look for a x value of 88. And a y value for 0.7. It is predicted to fall into place. 
  

## Model 2 SIM~GRIP



### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

The scatter plot above shows that the GRIP has a smaller correlation with SIMS vs ARM.


### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```


### Inferential  (Build model.2)
  
```{r}
model.2<- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
  
The information above shows us that adjusted r squared is 0.4053 and the residual standard error is 1.295, so the residual is larger for this grip data then the arm data. Both of these values indicate that model 1 is a better model. 
  

#### predict model.2 at target point
```{r}
predict(model.2,new,interval = "prediction")
```


#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

